% Created 2020-10-04 Sun 20:06
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{\today}
\title{An Intro to Data Science in Finance}
\hypersetup{
 pdfauthor={},
 pdftitle={An Intro to Data Science in Finance},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.1.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
If this works we can do the same MOOC with R.

\section{Week 1 (Setup)}
\label{sec:org61c7864}

\subsection{Session 1}
\label{sec:org73de0e0}

\begin{itemize}
\item Course Overview:  Note most other courses use stock data and create trading algos.  Here we are going to focus on core financial analyst tasks, e.g. what is the average PPP loan size in Texas?
\item Python Relative to other tools.
\begin{itemize}
\item Excel
\item Other Programming Languages
\item Comparison with R
\item Using Javascript for Visualization
\end{itemize}
\end{itemize}

\subsection{Session 2}
\label{sec:org4bba20a}

\begin{itemize}
\item Ways to run python
\begin{itemize}
\item Google's Colab and IPython
\item Locally
\begin{itemize}
\item The REPL
\item As a script file
\end{itemize}
\end{itemize}
\item Python Packages
\begin{itemize}
\item Extending the core language
\item Our most used packages.
\item Installing and Loading.
\end{itemize}
\end{itemize}

\subsection{Session 3}
\label{sec:orgf00e66d}

\begin{itemize}
\item An Introduction to Useful Packages:
\begin{itemize}
\item \href{https://pandas.pydata.org/}{Pandas}
\item \href{https://numpy.org/}{Numpy}
\item Scipy and Scikit Learn
\item Pytorch
\item Tensorflow and Keras
\end{itemize}
\end{itemize}

\section{Week 2 (Pandas and Data Description)}
\label{sec:org3b0425f}
Get spreadsheet type data and perform a corporate finance related task.
\subsection{Session 1}
\label{sec:org0b74b21}
\begin{itemize}
\item An intro to Pandas
\item Reading csv and excel files.
\begin{itemize}
\item Locally and over the web.
\end{itemize}
\end{itemize}

\subsection{Session 2}
\label{sec:orgdd30512}

\begin{itemize}
\item Example: PPP Loan Statistics by State
\end{itemize}

Alternative:
\begin{itemize}
\item What is the average price at which a power plant sells electricity?
\item What is the NPV of a Power Plant over a Year?
\end{itemize}

\subsection{Session 3}
\label{sec:orgb726fdc}
\begin{itemize}
\item Subsetting data
\item Pivot Tables
\item Summary Statistics
\end{itemize}


\section{Week 3 (Numpy/Scipy)}
\label{sec:org22cbb59}

\subsection{Session 1}
\label{sec:org1c901e2}

\begin{itemize}
\item An introduction to Application Programming Interfaces (APIs) and online
data
\begin{itemize}
\item Example: Coinbase API
\item Example: Interactive Brokers API
\item EIA API.
\end{itemize}
\item Connecting to databases.
\end{itemize}


\subsection{Session 2}
\label{sec:orgf217745}
\begin{itemize}
\item Example: Simple Regression, the CAPM.
\item Make it better with pytorch/pyro and the Kalman filter.
\end{itemize}

\subsection{Session 3}
\label{sec:orge2faade}
\begin{itemize}
\item Visualization:
\begin{itemize}
\item Matplotlib
\item Seaborn
\item Plotly
\item ggplot (using plotnine library)
\end{itemize}
\end{itemize}

\section{Week 4}
\label{sec:org726adbd}

Where to go from here.  How to share code, get help, and create reproducible
environments.

\subsection{Session 1}
\label{sec:orge423071}

Virtual Environments
\begin{itemize}
\item Ensuring compatible python and package versions.
\end{itemize}

\subsection{Session 2}
\label{sec:org57ff0d6}

\begin{itemize}
\item Git/Github and IDE Integration
\begin{itemize}
\item Why use version control?
\begin{itemize}
\item Collaborate with others more easily.
\item Show others your work.
\end{itemize}
\end{itemize}
\end{itemize}

\subsection{Session 3}
\label{sec:org6f8e51f}

\begin{itemize}
\item The Integrated Development Environment (IDE)
\begin{itemize}
\item What does an IDE provide?
\begin{itemize}
\item Code Completion
\end{itemize}
\item Git/Github and IDE Integration
\end{itemize}
\end{itemize}
\end{document}